Poseidon Adventure

### 2019-05-15 docs/index.Rmd
add lf samp visualizations

>>>>

<a href="https://sgaichas.github.io/poseidon-dev/CCAStdSurvLengthCompTest.html" target="_blank">CCA compare survey + sampled lengths with true - May 14, 2019</a>

<a href="https://sgaichas.github.io/poseidon-dev/NOBAStdSurvLengthCompTest.html" target="_blank">NOBA compare survey + sampled lengths with true - May 15, 2019</a>

<a href="https://sgaichas.github.io/poseidon-dev/NEUSStdSurvLengthCompTest.html" target="_blank">NEUS compare survey + sampled lengths with true - May 15, 2019</a>
